\thesistitle

### 2019-06-12 sections/research.tex
Nice formula

T2R Variability = (Diff(l) + Diff(v) + Diff(m))/Total(t)
Diff = Amount that differ from other clone instances in the clone class
Total = Total number in the clone instance
l = Number of literals
v = Number of variables
m = Number of method calls
t = Number of tokens

\paragraph{Literal variability}
We allow only variability in the value of literals, but not in the type of literals. This is because a difference in literal type may have a big impact on the refactorability of the cloned fragment. When we refactor literals that have both the same type, in case of an ``Extract Method'' refactoring, we create a method argument for this literal and pass the corresponding literal from cloned locations. However, if two literals have different types, this might not be possible (or will have a negative effect on the design of the system).

\paragraph{}

@@

@@

All data for our experiments, as displayed in chapter \ref{ch:results}, is measured over a corpus of Java projects. In this chapter we will explain how we prepared this corpus.

>>>>

$$T2R\ Variability\ Percentage=\frac{Diff(l) + Diff(v) + Diff(m)}{Total(t)}$$
$$Diff=Amount\ that\ differ\ from\ other\ clone\ instances\ in\ the\ clone\ class$$
$$Total\ =\ Total\ number\ in\ the\ clone\ instance$$
$$l=Number\ of\ literals$$
$$v=Number\ of\ variables$$
$$m=Number\ of\ method\ calls$$
$$t=Number\ of\ tokens$$

\noindent \textbf{Literal variability}\\
We allow only variability in the value of literals, but not in the type of literals. This is because a difference in literal type may have a big impact on the refactorability of the cloned fragment. When we refactor literals that have both the same type, in case of an ``Extract Method'' refactoring, we create a method argument for this literal and pass the corresponding literal from cloned locations. However, if two literals have different types, this might not be possible (or will have a negative effect on the design of the system).

\noindent \textbf{Variable variability}\\

@@

Mainly the requirement to have access to all external libraries is a difficult one to satisfy in diverse projects. Because of this, these definitions may be less suitable for large scale clone detection purposes.

@@

All results of our experiments, as displayed in chapter \ref{ch:results}, are measured over a corpus of Java projects. In this chapter we will explain how we prepared this corpus.
